```{r}
# Load dplyr for data manipulation and piping
library(dplyr)

# Make random number generation reproducible
set.seed(123)

# Number of observations/rows to generate
data_size <- 100

```

```{r}
# create the dataframe
df <- data.frame(
 age = round(rnorm(data_size, 35, 10)),
 income = round(rnorm(data_size, 50000, 15000)),
 education_years = sample(8:18, data_size, replace = TRUE),
 purchased = sample(c("No", "Yes"), data_size, replace = TRUE, prob = c(0.7, 0.3))
)

# Ensure the dependent variable is a factor
df$purchased <- as.factor(df$purchased)

# Check the structure of the data
str(df)
cat("\n\n")
summary(df)
```
```{r}
#head(x, rows)
head(df, 10)
```

Building logistic model using glm(family = "binomial")

Try to predict purchased based on age, income, and education_years:
```{r}
#build regression model,
#purchased ~ age + income + education_years

model <- glm(purchased ~ age + income + education_years,
             data=df, family = 'binomial')


#model <- glm(purchased ~ ., data = df, family = "binomial") if you want all variables, use a dot (.)
```

Summarizing and interpreting the model.

*Deviace Residuals:* indicate how well the mdoel is fit to the data, smaller is better. 

*Coefficients*
Estimates are log-odds. Highr log-odd estimate means that as predictor variable increases, so does the probability of a postive/"Yes" categorization from the model

std. Error is the standard error of the coefficient estimate (log-odds)

z-value, Wald Z-Stat, testing the significance of each coefficient/predictor

Pr(>|z|), the p-value. Default significance is 0.05, if its less than that then the model has shown the predictor is statistically significant.

*Null Deviance:* deviance of the model with only its intercept

*Residual Deviance:* deviance of the fitted model. if this value is significantly smaller than null deviance, then the predictors are suggested to be good for the model

*AIC* measure of fitness, penalizes model for complexity. lower AIC is indicative of a good model

```{r}
# get model summary
summary(model)
```
Interpret log-odds as odd ratios:
Odds ratio > 1 means that per one-unit increase in the predictor, the odds of the outcome ("Yes") increases by such a factor.

Odds ratio < 1 means the odds decrese

For example, an odds ratio of 1.2 means the odds increase by 20% for every one-unit increase in the predictor.
```{r}
# Calculate odds ratios
cat("Odds Ratios:\n")
exp(coef(model))
cat("\n\nConfidence Intervals:\n")
# You can also get confidence intervals for odds ratios
exp(confint(model))
```

We've built the model and interpreted the performance. Now, predictions.

```{r}
# Creating data for predictions
new_data <- data.frame(
  age = c(40, 25, 60),
  income = c(60000, 30000, 80000),
  education_years = c(16, 12, 18)
)

# Predictions, when we let type="response", we get a binary possibility
pred <- predict(model, newdata = new_data, type = 'response')
cat("Predictions:\n")
print(pred)
```
```{r}
# now, convert the probabilities into binary outcomes:
pred_classes <- ifelse(pred > 0.5, 'Yes', 'No')
cat("Binary Predictions:\n")
print(pred_classes)
```
Evaluation of model performance. For binary classification, a confusion matrix is common.

CM shows the counts of true/false positives/negatives. This allows us to calculate accuracy statistics like accuracy, precision, revall, F1.

```{r}
# build CM

# Get predictions from original dataset
predictions_on_df <- predict(model, type="response")

# make those og predicitons binary
predicted_classes_df <- ifelse(predictions_on_df > 0.5, "Yes", "No")

# ensure pred_og is a factor w/ the same levels as the df 
predicted_classes_df <- factor(predicted_classes_df , levels = levels(df$purchased))

# cm
cm <- table(Actual = df$purchased, Predicted = predicted_classes_df)

cat("Confusion Matrix:\n\n")
print(cm)

```
```{r}
#accuracy stats from cm

accuracy <- sum(diag(cm))/sum(cm)
cat("Model Accuracy: ", round(accuracy, 4), "\n")
```


